### 2016-01-18 paper.tex
Some rewording per @nearyvs suggestion

The present task was to acquire a new experimental dataset for the lower
solidity RM2 turbine at sufficient Reynolds numbers to be relevant to full-scale
modeling. It was hypothesized that the parasitic losses from rotor blade support
struts could play an important role in overall turbine performance. Thus, the
parasitic torque from strut drag was measured without blades, then deliberately
and significantly increased in the physical model to provide data to help answer
that question. The velocity field in the near-wake of the turbine was then
measured to compare with measurements from a higher solidity rotor in the same
experimental setup \cite{Bachant2015-JoT}, and provide validation data for
numerical models that predict wake flows, which determine turbine--turbine
interaction and optimal spacing for turbine arrays. This dataset, along with the
code for processing and visualization, is publicly available (licensed via
Creative Commons CC-BY for data and MIT license for code) as a Git repository on
GitHub (\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable
archive with a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.

>>>>

The present study was motivated by the need to acquire a new experimental
dataset for the lower solidity RM2 turbine at sufficient Reynolds numbers to be
relevant to full-scale modeling. It was hypothesized that the parasitic losses
from rotor blade support struts could play an important role in overall turbine
performance. Thus, the parasitic torque from strut drag was measured without
blades, then deliberately and significantly increased in the physical model to
provide data to investigate its importance. The velocity field in the near-wake
of the turbine was then measured to compare with measurements from a higher
solidity rotor in the same experimental setup \cite{Bachant2015-JoT}, and
provide validation data for numerical models that predict wake flows, which
determine turbine--turbine interaction and optimal spacing for turbine arrays.
This dataset, along with the code for processing and visualization, is publicly
available (licensed via Creative Commons CC-BY for data and MIT license for
code) as a Git repository on GitHub
(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable archive with
a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
